IARC Technical Paper

### 2017-05-31 IARC_Paper/Paper.tex
Take out kill switch because Samid said so
Profread paper

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\geometry{letterpaper}
\usepackage{doc}
\usepackage{url}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{gensymb}
\usepackage[section]{placeins}
\usepackage{fancyhdr}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
     text centered, rounded corners, minimum height=2em]
\tikzstyle{line} = [draw, -latex']
\usepackage{hyperref}
\usepackage[belowskip=-50pt,aboveskip=2pt]{caption}
% \setlength{\intextsep}{8pt plus 2pt minus 2pt}

@@

\abstract{
Texas Aerial Robotics will compete in Mission 7 of the International Aerial Robotics Competition (IARC) in 2017. Our goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter equipped with a Logitech C210 camera for vision, a Nvidia Jetson for vision processing, and a Pixhawk for controlling the quadcopter. The mission takes place in a GPS denied environment, so gridlines will be used as reference positions. 
}

@@

\section{Introduction}
\subsection{The Mission}
Mission 7a of IARC consists of developing an aerial vehicle that can interact with moving ground robots. These ground robots, or Roombas, have randomized movements so the aerial vehicle must make decisions on the fly rather than having preprogrammed instructions. The vehicle must herd the 10 Roombas across one side of the 20 meter by 20 meter grid. Additionally, 4 obstacle Roombas have PVC poles the vehicle must avoid. The way the vehicle must herd the Roombas is by either blocking the forward motion of the Roomba, directing it to rotate 180\degree, or tapping the pressure plate atop the Roomba, directing the Roomba to rotate 45\degree clockwise.

An added difficulty to the mission is that the setting is a (Global Positioning System) GPS denied environment. Additionally, there are no landmark features to allow the vehicle to use Simultaneous Localization and Mapping (SLAM) for orientating itself on the grid. Thus, we determined that we needed to design other methods to determine our positioning. By using a camera to observe the gridlines and an Inertial Measurement Unit (IMU), we are working our way to determining where the vehicle is on the grid.

@@

\subsection{Yearly milestones}
This is the first time Texas Aerial Robotics is competing in any event. Our goal for the year was to be competitive at this year's IARC.

\subsection{Faculty Support}
At the beginning of the creation of Texas Aerial Robotics, the team searched for professors to provide technical guidance for the project. Within the UT Department of Aerospace TAR reached out to Dr. Maruthi Akella. Dr. Akella has been conducting research in areas similar to the core objectives of IARC’s Mission 7. Dr. Akella has been doing research to create agile intelligent quadrotors in environments free of GPS. Dr. Akella expressed interest in Mission 7 as soon the team reached out. From the outset of the relationship Dr. Akella has provided expertise, access to his grad students as well as access to his indoor and outdoor lab. Dr. Akella also introduced us to multiple corporation looking to sponsor student projects. TAR is incredibly thankful to have the support of Dr. Akella.

\subsection{Team Structure}
As important as the drone a team develops, is the process in which it is developed. The past year has been Texas Aerial Robotics(TAR) maiden year and the team has put a lot of effort in developing the process to catalyze the engineering of the drone. During the fall semester, the team made just about every mistake in the book with regards to how to run a competition team. The team struggled with communication, vision and drive. This disorganization resulted with TAR ending the first semester with little to no progress. With the failure of the semester came the resignation of our president. Texas Aerial Robotics was at a crossroads.

The winter break was used as a period of reflection. At the start of the new semester a new president was elected and a formal management style was implemented: Scrum. This is short term, agile style of management that makes short term goals and reflects and resets for the next “scrum”. Along with scrum, the team implemented organizational apps such as Slack and Trello. Slack allowed the team to keep all the sub-team conversations separate, but unified. This kept members from silencing their line of communication as well as still allowing members to view what the other sub-teams are working on. Automated reminders for meetings were also set up through Slack to prevent members from forgetting their duties to the team. Trello was an incredible addition to our organizational platform. Trello is a ubiquitous bulletin board in which we can make and assign tasks throughout the team. This has helped to promote accountability as well as allow the better delegation of jobs. Finally, the last big productivity mechanism we implemented was the formation of a business/logistics subteam. This team has allowed the engineers to focus on engineering by acquiring money and organizing logistics, such as the trip to Atlanta.

@@

After our initial brainstorming period the team decided that the drone would would need to be able to easily interact with Roombas, fly at least 10 min and have a large body to accommodate for the many electronics. At the beginning of our design process the team was faced with the prospects of buying, or designing and building a drone in house. After doing research, the design team decided that no prebuilt could fully meet the needs. The team decided to use the propeller guards as a forward blocking surface as well as a safety feature. To get the propeller guards to the required height to block the Roombas the team chose to have the body of the drone be the landing gear. Surface area of the drone was elected to be maximized to decrease the precision needed to contact the top of the Roombas. The quadcopter would be made with aluminum arms with a carbon fiber base to minimize weight and maximize strength and build quality. During build, we laser-cut wood for the base to allow for rapid iterating. Rapid iteration was instrumental in finding the optimal layout of electronics as well as flush out design flaws. Using wood also meant that we would be dealing with more magnetic interference and vibration than we would after switching to carbon fiber, allowing us to test with worse conditions. The body of the drone was designed from the outset to keep the electronics easily accessible. For this reason a removable base cover was implemented.

We decided to fabricate a quadcopter with aluminum arms with a carbon fiber base. During build, we laser-cut wood for the base to allow for rapid iterating. Using wood also meant that we would be dealing with more magnetic interference and vibration than we would after switching to carbon fiber, allowing us to test with worse conditions. Our quadrotor needed to house all of the sensors for operation with sufficient flight time.

@@

\subsection{Hardware} 
At the end of the aluminum arms sit four Tiger MT2216 v2 motors with 12in plastic props for lift. The four motors provide 2.25 kilograms of lift at 65\% throttle, a sufficient amount for our sightly under 2 kilogram quadcopter. The arms are fixed into the base pieces, which do not pass enough vibration to the sensors that we needed any additional vibration damping.

@@

Both the optical flow sensor and the LIDAR sensor integrate with the Arducopter flight software that is running on the Pixhawk. The optical flow sensor is mounted on the side of the main body of the quadcopter to ensure that sensor receives adequate lighting at all times. 
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
    % Place nodes
    \node [block] (battery) {Battery};
    \node [block, below of=battery] (siphon) {Power siphon};
    \node [block, below of=siphon] (Pixhawk) {Pixhawk};
    \node [block, below right of=battery, xshift=3cm, align=center] (PDB) {Power Distribution \\ Board};
    \node [block, below left of=battery, xshift=-3cm] (Jetson) {Nvidia Jetson TX1};
    \node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
    \node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
    \node [block, below of=Jetson] (Camera) {Camera};
    \node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
    \node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
    \node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LIDAR) {LIDAR};
    \node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
    % Draw edges
    \path [line] (battery) -- (siphon);
    \path [line] (siphon) -- (Pixhawk);
    \path [line] (battery) -- (PDB);
    \path [line] (PDB) -- (ESCs);
    \path [line] (battery) -- (Jetson);
    \path [line] (Camera) -- (Jetson);
    \path [line, dashed] (Flow) -- (Pixhawk);
    \path [line, dashed] (Jetson) -- (Pixhawk);
    \path [line, dashed] (LIDAR) -- (Pixhawk);
    \path [line, dashed] (Pixhawk) -- (Telemetry);
    \path [line, dashed] (Spektrum) -- (Pixhawk);
    \path [line, dashed] (Pixhawk) -- (ESCs);
    \path [line] (ESCs) -- (Motors);
\end{tikzpicture}
\caption*{Solid arrows indicate power while dashed lines indicate power+data}
\end{center}
\end{figure}
\subsection{Vision}

@@

\subsection{Kill Switch}
Hopefully we will have a Kill Switch

\subsection{Prop Guards}
Our prop guards took multiple iterations. We wanted a design that would not interfere with the prop wash, but still be able to avoid the quadcopter from destroying itself in the unfortunate event it collides with something. The first iteration looked nice, but interfered with the prop wash too much and weighted too much, reducing the thrust.

>>>>

\documentclass[12pt]{article}
\usepackage[margin=1in]{geometry}
\geometry{letterpaper}
\usepackage{doc}
\usepackage{url}
\usepackage{lastpage}
\usepackage{graphicx}
\usepackage{gensymb}
\usepackage[section]{placeins}
\usepackage{fancyhdr}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\tikzstyle{block} = [rectangle, draw, fill=blue!20, 
     text centered, rounded corners, minimum height=2em]
\tikzstyle{line} = [draw, -latex']
\usepackage{hyperref}
\usepackage[belowskip=-22pt,aboveskip=2pt]{caption}
% \setlength{\intextsep}{8pt plus 2pt minus 2pt}

@@

\abstract{
Texas Aerial Robotics will compete in Mission 7 of the International Aerial Robotics Competition (IARC) in 2017. Our goal is to direct Roombas (iRobot Create 2's), known as ground robots, using a quadcopter equipped with a Logitech C210 camera for vision, a Nvidia Jetson TX1 for vision processing, and a Pixhawk for controlling the quadcopter. The mission takes place in a GPS denied environment, so gridlines will be used as reference positions. 
}

@@

\section{Introduction}
\subsection{The Mission}
Mission 7a of IARC consists of developing an aerial vehicle that can interact with moving ground robots. These ground robots, or Roombas, have randomized movements so the aerial vehicle must make decisions on the fly rather than having preprogrammed instructions. The vehicle must herd the 10 Roombas across one side of the 20 by 20 square meter grid. Additionally, 4 obstacle Roombas have PVC poles the vehicle must avoid. The way the vehicle must herd the Roombas is by either blocking the forward motion of the Roomba, directing it to rotate 180\degree, or tapping the pressure plate atop the Roomba, directing the Roomba to rotate 45\degree clockwise.

An added difficulty to the mission is that the setting is a Global Positioning System (GPS) denied environment. Additionally, there are no landmark features to allow the vehicle to use Simultaneous Localization and Mapping (SLAM) for orientating itself on the grid. Thus, we determined that we needed to design other methods to determine our positioning. By using a camera to observe the gridlines and an Inertial Measurement Unit (IMU), we are working our way to determining where the vehicle is on the grid.

@@

\subsection{Yearly Milestones}
This is the first time Texas Aerial Robotics is competing in any event. Our goal for the year was to be competitive at this year's IARC. %Add more here

\subsection{Faculty Support}
At the beginning of the creation of Texas Aerial Robotics, the team searched for professors to provide technical guidance for the project. TAR reached out to Dr. Maruthi Akella, a professor at UT Austin's Aerospace Engineering Department. Dr. Akella has been conducting research in areas similar to the core objectives of IARC’s Mission 7. Dr. Akella has been doing research to create agile intelligent quadrotors in environments free of GPS. Dr. Akella expressed interest in Mission 7 as soon the team reached out. From the outset of the relationship Dr. Akella has provided expertise, access to his grad students, as well as access to his indoor and outdoor lab. Dr. Akella also introduced us to multiple corporations looking to sponsor student projects. TAR is incredibly thankful to have the support of Dr. Akella.

\subsection{Team Structure}
As important as the drone a team develops, is the process in which it is developed. The past year has been Texas Aerial Robotics (TAR) maiden year, and the team has put a lot of effort in developing the process to catalyze the engineering of the drone. During the fall semester, the team made just about every mistake in the book with regards to how to run a competition team. The team struggled with communication, vision and drive. This disorganization resulted with TAR ending the first semester with little to no progress. With the failure of the semester came the resignation of our president. Texas Aerial Robotics was at a crossroads.

The winter break was used as a period of reflection. At the start of the new semester a new president was elected and a formal management style was implemented: Scrum. This is an agile style of management that makes short term goals and reflects and resets for the next “scrum”. Along with scrum, the team implemented organizational apps such as Slack and Trello. Slack allowed the team to keep all the sub-team conversations separate, but unified. This kept members from silencing their line of communication as well as still allowing members to view what the other sub-teams are working on. Automated reminders for meetings were also set up through Slack to prevent members from forgetting their duties to the team. Trello was an incredible addition to our organizational platform. Trello is a ubiquitous bulletin board in which we can make and assign tasks throughout the team. This has helped to promote accountability as well as allow the better delegation of jobs. Finally, the last big productivity mechanism we implemented was the formation of a business/logistics subteam. This team has allowed the engineers to focus on engineering by acquiring money and organizing logistics, such as the trip to Atlanta.

@@

After our initial brainstorming period the team decided that the drone would need to be able to easily interact with Roombas, fly at least 10 minutes and have a large body to accommodate for the many electronics. At the beginning of our design process the team was faced with the prospects of buying, or designing and building a drone in house. After doing research, the design team decided that no prebuilt quadcopter could fully meet the needs. The team decided to use the propeller guards as a forward blocking surface as well as a safety feature. To get the propeller guards to the required height to block the Roombas the team chose to have the body of the drone be the landing gear. Surface area of the drone was elected to be maximized to decrease the precision needed to contact the top of the Roombas. The quadcopter would be made with aluminum arms with a carbon fiber base to minimize weight and maximize strength and build quality. During build, we laser-cut wood for the base to allow for rapid iterating. Rapid iteration was instrumental in finding the optimal layout of electronics as well as flush out design flaws. Using wood also meant that we would be dealing with more magnetic interference and vibration than we would after switching to carbon fiber, allowing us to test with worse conditions. The body of the drone was designed from the outset to keep the electronics easily accessible. For this reason a removable base cover was implemented.

@@

% \subsection{Hardware} 
At the end of the aluminum arms sit four Tiger MT2216 v2 motors with 12in plastic props for lift. The four motors provide 2.25 kilograms of lift at 65\% throttle, a sufficient amount for our sightly under 2 kilogram quadcopter. The arms are fixed into the base pieces, which do not pass enough vibration to the sensors that we needed any additional vibration damping.

@@

Both the optical flow sensor and the LIDAR sensor integrate with the Arducopter flight software that is running on the Pixhawk. The optical flow sensor is mounted on the side of the main body of the quadcopter to ensure that sensor receives adequate lighting at all times. 
\begin{figure}[!htbp]
\begin{center}
\begin{tikzpicture}[node distance = 1.5cm and 8cm, auto]
    % Place nodes
    \node [block] (battery) {Battery};
    \node [block, below of=battery] (siphon) {Power siphon};
    \node [block, below of=siphon] (Pixhawk) {Pixhawk};
    \node [block, below right of=battery, xshift=3cm, align=center] (PDB) {Power Distribution \\ Board};
    \node [block, below left of=battery, xshift=-3cm] (Jetson) {Nvidia Jetson TX1};
    \node [block, right of=Pixhawk, xshift=2.6cm] (ESCs) {ESCs};
    \node [block, below right of=ESCs, xshift=.5cm] (Motors) {Motors};
    \node [block, below of=Jetson] (Camera) {Camera};
    \node [block, below right of=Pixhawk, yshift=-1cm] (Flow) {PX4FLOW};
    \node [block, below right of=Pixhawk, xshift=3.5cm, yshift=-1cm] (Spektrum) {Spektrum controller};
    \node [block, below left of=Pixhawk, xshift=-.5cm, yshift=-1cm] (LIDAR) {LIDAR};
    \node [block, below left of=Pixhawk, xshift=-3.5cm, yshift=-1cm] (Telemetry) {Ground Telemetry};
    % Draw edges
    \path [line] (battery) -- (siphon);
    \path [line] (siphon) -- (Pixhawk);
    \path [line] (battery) -- (PDB);
    \path [line] (PDB) -- (ESCs);
    \path [line] (battery) -- (Jetson);
    \path [line, dashed] (Camera) -- (Jetson);
    \path [line, dashed] (Flow) -- (Pixhawk);
    \path [line, dashed] (Jetson) -- (Pixhawk);
    \path [line, dashed] (LIDAR) -- (Pixhawk);
    \path [line, dashed] (Pixhawk) -- (Telemetry);
    \path [line, dashed] (Spektrum) -- (Pixhawk);
    \path [line, dashed] (Pixhawk) -- (ESCs);
    \path [line] (ESCs) -- (Motors);
\end{tikzpicture}
\caption*{Flowchart of quadcopter electronics \\ \tiny *Solid arrows indicate power while dashed lines indicate power+data}
\end{center}
\end{figure}
\subsection{Vision}

@@

% \subsection{Kill Switch}
% Hopefully we will have a Kill Switch

\subsection{Prop Guards}
Our prop guards took multiple iterations. We wanted a design that would not interfere with the prop wash, but still be able to avoid the quadcopter from destroying itself in the unfortunate event it collides with something. The first iteration looked nice, but interfered with the prop wash too much and weighed too much, reducing the thrust.
